\documentclass[a4paper,11pt]{article}
\usepackage{geometry,graphicx,multirow,algorithm,algorithmic,amsmath,dsfont,tikz,subfigure,lscape,array,listings,textcomp,hyperref,color,amsthm}
\geometry{a4paper}
\usetikzlibrary{shapes,calc}
\setlength{\parindent}{0pt}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\baselinestretch}{2}

\begin{document}

\begin{center}
The most important current threats to biodiversity
\end{center}

{\color{blue}Although} biodiversity is {\color{red}very important for human well-being, research studies carry out} that the {\color{red}variety in} species {\color{red}poses major threats}. %21 
In this paragraph, some of these studies are cited, and {\color{red}specific examples} are given. %14
First of all, many animals and plants die due to {\color{red}habitat destruction}. %12
By building cities on farmland, nearly {\color{red}half of} the prime main {\color{red}agricultural land} in California is eliminated; by {\color{red}clearing forests} for timber, {\color{red}large areas} of the {\color{red}Brazilian rainforest} are destroyed (Harris 2002; Pearce \& Williams 2008). %36
{\color{blue}In addition}, the over-exploitation of species can cause elimination. %13
In Newfoundland, Canada, {\color{red}for example}, the {\color{red}local ecosystem changed considerably}, because the cod disappeared in the 20th century, due to {\color{red}intense overfishing} (Chen et al. 2009).  %26
{\color{blue}Furthermore}, {\color{red}climate change} causes {\color{red}higher temperatures}, which can kill {\color{red}animal} and {\color{red}plant species}. %13 
Akin (2010) {\color{green}argued that} {\color{red}hibernating animals} may {\color{red}wake early} because of warmth, but starve {\color{red}in the absence of} food. %19
{\color{blue}Finally}, pollution threatens biodiversity. %4
{\color{red}For example}, Pearce \& Williams (2008) {\color{green}investigated} the Amoco Cadiz case. %11
This {\color{red}very large crude carrier ran aground on} Portsall Rocks, France, in 1978, and {\color{red}split in three}. %17
About 0.25 million tonnes of {\color{red}crude oil} were spilled, resulting in {\color{red}enormous damage to the environment}. %16
{\color{blue}In addition}, {\color{red}environmental pollution} is caused by the {\color{red}widespread use} of pesticides on farmland. %14
For instance, Chen et al. (2009) claimed that vultures {\color{red}take up pesticides} from grass via {\color{red}dead cows}, {\color{red}resulting in} a {\color{red}considerable decline of} this population in India. % 27
{\color{blue}Hence}, the threats, {\color{red}stated above}, have {\color{red}serious consequences} for the biodiversity in certain regions. %14

Word count: 254 words. WA2, Thea Vuik, 863037
\end{document}
