\documentclass[a4paper,10pt]{article}
\usepackage{geometry,graphicx,multirow,algorithm,algorithmic,amsmath,dsfont,tikz,subfigure,lscape,array,listings,textcomp,hyperref,color,amsthm}
\geometry{a4paper}
\usetikzlibrary{shapes,calc}
\setlength{\parindent}{0pt}
\definecolor{dkgreen}{rgb}{0,0.6,0} \definecolor{gray}{rgb}{0.5,0.5,0.5}
\makeatletter	% References to subfigures without brackets
\renewcommand{\thesubfigure}{\alph{subfigure}}
\renewcommand{\@thesubfigure}{(\alph{subfigure})\hskip\subfiglabelskip}
\renewcommand{\@@thesubfigure}{(\alph{subfigure})}
\makeatother
\pagestyle{myheadings}
\newtheoremstyle{discussion_style}  % name of the style to be used
  {}       % measure of space to leave above the theorem. E.g.: 3pt
  {}       % measure of space to leave below the theorem. E.g.: 3pt
  {}   % name of font to use in the body of the theorem
  {}        % measure of space to indent
  {}  % name of head font
  {:}   % punctuation between head and body
  {\newline}       % space after theorem head
  {}           % Manually specify head

\theoremstyle{discussion_style} \newtheorem{discussion}{\color{red}{Discussion point}}
\newtheoremstyle{theorem_style}  {}    {}   {}  {}      {\bfseries}    {}    {\newline}  {} 
\theoremstyle{theorem_style} \newtheorem{theorem}{Theorem}
\newcommand{\bb}[1]{\boldsymbol{\mathbf{#1}}}
\markright{{Thea Vuik, Unit4.pdf, \today}}
\begin{document}
\begin{itemize}
\item The company has to be prepared, \ldots speaking, to leap into the dark.
\item The agreement doesn't allow you to \ldots business from your home.
\item The organization has promised to eliminate cumbersome and unnecessary \ldots.
\item The ability to \ldots and evaluate information.
\item The collection and \ldots of data.
\item Several of the newspapers were \ldots his resignation.
\item They were symbols of the fact that Osiris brought life by growing food -- 'the body of the god on whom one feeds', thus providing eternal \ldots and the hope of eternal life.
\item This film was a \ldots in the history of cinema.
\item She cites other scholars' work only \ldots it supports her own theories.
\item \ldots should ideally not exceed income.
\item \ldots one's thoughts.
\item The newspaper aims to cover a \ldots range of issues.
\item His \ldots government has reduced the nation to poverty and desperation.
\item The report \ldots that a world recession was unlikely.
\item The castle stood in a \ldots position on the harbour.
\item The \ldots structure of medieval society.
\item Compare and \ldots the two main characters in the play. 
\item The court \ldots the argument and found the defendant not guilty.
\item He certainly doesn't fit the \ldots of the emotional Italian.
\item The 1980s were \ldots by high inflation and high unemployment.
\end{itemize}

\newpage
\begin{itemize}
\item metaphorically
\item conduct
\item bureaucracy
\item analyse
\item classification
\item calling for
\item sustenance
\item milestone
\item insofar as
\item Expenditure
\item Embody
\item diverse
\item autocratic
\item concluded
\item strategic
\item hierarchical
\item contrast
\item rejected
\item stereotype
\item characterized
\end{itemize}
\end{document}
