\documentclass[a4paper,10pt]{article}
\usepackage{geometry,graphicx,multirow,algorithm,algorithmic,amsmath,dsfont,tikz,subfigure,lscape,array,listings,textcomp,hyperref,color,amsthm}
\geometry{a4paper}
\usetikzlibrary{shapes,calc}
\setlength{\parindent}{0pt}
\definecolor{dkgreen}{rgb}{0,0.6,0} \definecolor{gray}{rgb}{0.5,0.5,0.5}
\makeatletter	% References to subfigures without brackets
\renewcommand{\thesubfigure}{\alph{subfigure}}
\renewcommand{\@thesubfigure}{(\alph{subfigure})\hskip\subfiglabelskip}
\renewcommand{\@@thesubfigure}{(\alph{subfigure})}
\makeatother
\pagestyle{myheadings}
\newtheoremstyle{discussion_style}  % name of the style to be used
  {}       % measure of space to leave above the theorem. E.g.: 3pt
  {}       % measure of space to leave below the theorem. E.g.: 3pt
  {}   % name of font to use in the body of the theorem
  {}        % measure of space to indent
  {}  % name of head font
  {:}   % punctuation between head and body
  {\newline}       % space after theorem head
  {}           % Manually specify head

\theoremstyle{discussion_style} \newtheorem{discussion}{\color{red}{Discussion point}}
\newtheoremstyle{theorem_style}  {}    {}   {}  {}      {\bfseries}    {}    {\newline}  {} 
\theoremstyle{theorem_style} \newtheorem{theorem}{Theorem}
\newcommand{\bb}[1]{\boldsymbol{\mathbf{#1}}}
\markright{{Thea Vuik, Unit3.pdf, \today}}
\begin{document}
\begin{itemize}
\item It would be more \ldots to switch the machine off at night.
\item It is generally thought that there were pictographic and \ldots origins for a large number of symbols that turn up in later writing systems.
\item This section provides a \ldots framework for the tasks.
 \item The building work was \ldots by a local contractor.
\item They \ldots such great enjoyment from these simple games.
\item It's difficult to \ldots the cost of making your house safe.
\item This meeting has great \ldots importance for the people of Ireland. 
 \item Remote voting via the Internet is \ldots to absentee voting and will have the same kinds of problems.
\item She rebelled against \ldots and refused to marry.
\item The accident caused \ldots damage to both cars.
\item It would be a \ldots if we didn't qualify for the World Cup next year.
\item The \ldots developed by John Kelly involves negotiating the syllabus with students and sponsors.
\item I don't want to talk about \ldots situations.
\item The novel did not really exist as a \ldots before the 17th century.
\item They revealed in their studies that newer titles are \ldots richer and are characterised by an increasing \ldots fullness.
\item His suggestions may be seen as an \ldots criticism of government policy.
\item These latest figures \ldots the view that economic growth is slowing.
\item Make a \ldots for you writing.
\item Many of the academic texts that you read and write will have \ldots within the text and a reference list at the end of the text.
\item A \ldots hole that no one would notice.
\item The performance of each employee is \ldots once a year.
\item Davenport still stands at number one in the world \ldots.
\item Home visits by staff are an \ldots part of the service.
\item Hundreds of people \ldots refuge in the British Embassy.
\item There was a long list of \ldots at the end of the paper.
\item Recent \ldots on cancer emphasizes the importance of diet.
\end{itemize}

\newpage
\begin{itemize}
\item economical
\item ideographic
\item conceptual
 \item carried out
\item derive 
\item estimate
\item symbolic
 \item analogous
\item convention
\item extensive
\item catastrophe
\item methodology
\item hypothetical
\item genre
\item semantically syntactic
\item implicit
\item reinforce
\item skeleton plan
\item in-text references
\item microscopic hole
\item evaluated
\item rankings
\item integral
\item sought
\item references
\item literature
\end{itemize}

\end{document}
