\documentclass[a4paper,10pt]{article}
\usepackage{geometry,graphicx,multirow,algorithm,algorithmic,amsmath,dsfont,tikz,subfigure,lscape,array,listings,textcomp,hyperref,color,amsthm}
\geometry{a4paper}
\usetikzlibrary{shapes,calc}
\setlength{\parindent}{0pt}
\definecolor{dkgreen}{rgb}{0,0.6,0} \definecolor{gray}{rgb}{0.5,0.5,0.5}
\makeatletter	% References to subfigures without brackets
\renewcommand{\thesubfigure}{\alph{subfigure}}
\renewcommand{\@thesubfigure}{(\alph{subfigure})\hskip\subfiglabelskip}
\renewcommand{\@@thesubfigure}{(\alph{subfigure})}
\makeatother
\pagestyle{myheadings}
\newtheoremstyle{discussion_style}  % name of the style to be used
  {}       % measure of space to leave above the theorem. E.g.: 3pt
  {}       % measure of space to leave below the theorem. E.g.: 3pt
  {}   % name of font to use in the body of the theorem
  {}        % measure of space to indent
  {}  % name of head font
  {:}   % punctuation between head and body
  {\newline}       % space after theorem head
  {}           % Manually specify head

\theoremstyle{discussion_style} \newtheorem{discussion}{\color{red}{Discussion point}}
\newtheoremstyle{theorem_style}  {}    {}   {}  {}      {\bfseries}    {}    {\newline}  {} 
\theoremstyle{theorem_style} \newtheorem{theorem}{Theorem}
\newcommand{\bb}[1]{\boldsymbol{\mathbf{#1}}}
\markright{{Thea Vuik, Unit5.pdf, \today}}
\begin{document}
\begin{itemize}
\item \ldots is information relating to numbers or amounts.
\item We offer a \ldots range of goods and services.
\item They \ldots with each other via email.
\item A territorial \ldots between rival gangs.
\item What are the difficulties you are most likely to \ldots? 
\item We are still hopeful that further talks will result in a \ldots.
\item The first two years of study provide a solid \ldots in computing.
\item We shall have to make some \ldots changes in the way we do business.
\item The extreme \ldots of old people to crime.
\item Fresh water and medicines were \ldots in the disaster area.
\item We hadn't grasped the \ldots of the task we were facing.
\item Difficulties were caused by the \ldots of the legislation.
\item Freud's ideas \ldots our understanding of the mind.
\item Similar trends may be \ldots in most modern societies.
\item \ldots few women become airline pilots.
\item The document \ldots our company's recycling policy.
\item "It is a good figure but \ldots you have to say the trend remains flat and that we are still bumping along the bottom," said John Shepperd.
\item \ldots is information relating to what something or someone is like.
\item The \ldots complexity and dramatic lighting of the staircase at Windsor had been achieved by May on a smaller scale at the earlier Eltham Lodge.
\item The treatment has no significant \ldots.
\item No one was behind it, but in the rear wall of the office I noticed, for the first time, a door which had been left \ldots open.
\item The Cup Final was \ldots via satellite to over 20 countries.
\item Scientists are attempting, by genetic \ldots, to produce more effective vaccines.
\item Alice can look after the children. She's very \ldots.
\end{itemize}

\newpage
\begin{itemize}
\item Quantitative data
\item comprehensive
\item communicate
\item dispute
\item encounter
\item consensus
\item foundation
\item fundamental
\item vulnerability
\item scarce
\item magnitude
\item complexity
\item revolutionized
\item observed
\item Relatively
\item outlines
\item objectively
\item Qualitative data
\item spatial
\item side effects
\item partially
\item transmitted
\item manipulation
\item reliable
\end{itemize}
\end{document}
